---
title: "Practice Activity 9.1 Andrew Martinez"
format:
 html:
  self-contained: true
editor: visual
---

## Practice Activity 9.1

## Loading In Data

```{r}
library(dplyr)
library(here)
library(tidyverse)
mystery_animal <- read.csv(here::here("supporting_artifacts", "Learning Targets", "mystery_animal.csv"))
```

## Linear Regression

```{r}
duck_diet_reg <- lm(weight_after~ weight_before, data = mystery_animal)
```

## Residuals

```{r}
plot(duck_diet_reg)
```

## 9.2 Practice Activity

-   Trombones weights are Normally distributed, with a mean weight of 4.6 pounds and a standard deviation of 0.8 pounds.

-   Trumpet weights are Uniformly distributed between 1.5 and 3.5 pounds.

-   Reed instruments (like clarinets, bassoons, and saxophones) have weights that are Chi-Square distributed with 4 degrees of freedom

## Warm-Up

```{r}

qnorm(.95, mean = 2.5, sd = 1)

qnorm(.1, mean = 4.6, sd = .8)

pnorm(.5, mean = 2.5, sd = 1)



```

## Function

```{r}

music_man <- function(n_tromb, n_cor, n_reed){
  
  trombones <- rnorm(n_tromb, mean = 4.6, sd = .8)
  cornets <- runif(n_cor, min = 1.5, max = 3.5)
  reeds <- rchisq(n_reed, df = 4)
  weight <- sum(trombones,cornets,reeds)
  
  return(weight)
  
}

set.seed(1957)

my_weights <- rerun(.n = 1000, 
                    music_man(n_tromb = 76, n_cor = 110, n_reed = 1035)
                    ) |> 
  flatten_dbl()
p = sum(my_weights < 4532)
```

## 
