---
title: "Lab 9 Andrew Martinez"
format:
 html:
  code-fold: true
  self-contained: true
editor: visual
---

## Libraries And Loading In Dataset

```{r}
#| message: false
library(tidyverse)
library(here)
StateNamesA <- read_csv(here::here("supporting_artifacts", 
                                   "Lab & Challenge 9", 
                                   "StateNames_A.csv"))
```

## Filtering For Allison's By State

```{r}
#| echo: false
StateNamesA <- StateNamesA |> 
  rename("Sex at Birth" = "Gender") 
StateNamesA |> 
  pivot_wider(
    names_from = `Sex at Birth`,
    values_from = Count) |> 
  filter(Name == "Allison") |> 
  group_by(State) |> 
  summarize(across(F:M, sum)) |> 
  mutate(across(F:M, ~replace_na(.,0)))
  
```

## Visualization of Allison's

```{r}
Summation_Of_Allisons <- StateNamesA |> 
  filter(`Sex at Birth` == "F",
          Name == "Allison") |> 
  group_by(Year) |> 
  summarize(Sum_Allison = sum(Count))

Summation_Of_Allisons |> 
  ggplot(mapping = aes(x = Year, y = Sum_Allison)) + 
  geom_col() +
  labs(title = "Number of Females Named Allison per Year in the US",
       y = "")
```

## Modeling

```{r}
##Used Mcgritter Pipe so data = . Works
Regression_Allison <- StateNamesA |> 
  filter(Name == "Allison",
        `Sex at Birth` == "F") %>%
  lm(Count ~ Year, data = .)

Regression_Allison |> 
  broom::augment() |> 
  ggplot(mapping = aes(x = Year, y = .fitted)) + 
  geom_point()
```

## Regression Equation:

### Y-Hat: 3881.886 - 1.876(Year)

## Plot of Residuals

```{r}
Regression_Allison |> 
  broom::augment() |> 
  ggplot(mapping = aes(x = .fitted, y = .resid)) +
  geom_point()+
  labs(y = "Residual Values", x = "Fitted Values", title = "Visualization Of Residuals Vs Fitted Values")
```

## Residual Analysis:

The vast majority of residuals reside around zero and appear to be random in nature. Because of this, it is reasonable to conclude that the model has a linear relationship. Additionally, one could make the argument for a slight negative linear trend because the outliers at the top left of the plot.

## Question 8:

Upon analyzing the slope, the model tells us that the number of females at birth named Allison decreases by an average of -1.876 each additional year. In this scenario, the intercept is negligible as it represents the total number of females at birth named Allison in a state at year zero.

## Spelling By State (Allen's)

```{r}
#| message: false
StateNamesA |> 
  filter(`Sex at Birth` == "M",
         Name %in% c("Allan", "Alan", "Allen")) |>
  ggplot(mapping = aes(x = Year, y = Count, color = Name)) +
  geom_smooth() +
  labs(title = "Occurencies Of Different Spellings Of Allen Over Time")
  
```

```{r}
StateNamesA |> 
  filter(`Sex at Birth` == "M",
         Name %in% c("Allan", "Alan", "Allen")) |> 
  pivot_wider(
    names_from = Name,
    values_from = Count) |> 
  filter(
    Year == 2000,
    State %in% c("PA", "CA")) |>
  mutate(
    across(Allan:Allen, ~replace_na(., 0)),
    AllenPercentage = round(Allen/ rowSums(across(Allen:Allan)), 2),
    AlanPercentage = round(Alan/ rowSums(across(Allen:Allan)), 2),
    AllanPercentage = round(Allan/ rowSums(across(Allen:Allan)), 2),
  ) |> 
  subset(select = -c(1,2))
  
```
