---
title: "Lab 4 Stat 331 Andrew Martinez"
format:
  html:
    code-fold: true
    self-contained: true
editor: visual
---

## Loading In Data & Libraries

```{r}
#| message: false
library(tidyverse)
library(here)
avocado <- read_csv(here::here("supporting_artifacts", "Lab & Challenge 4",
                              "avocado.csv"))
```

## Identifying Important Regions

```{r}
library(dplyr)

avocado_major_regions <- data.frame(
  region = c("Midsouth", "Northeast", "Plains", "Southeast", "West", "SouthCentral", "GreatLakes", "WestTexNewMexico" )
)

avocado_cali_regions <- data.frame(
  region = c("SanFrancisco", "LosAngeles", "SanDiego","Sacramento"))

avocado_states <- data.frame(
  region = c("California", "NewYork", "SouthCarolina"))

## Renaming Avocado Sizes
avocado <- avocado |> 
  rename("small" = `4046`, "large" = `4225`, "extralarge" = `4770`) |> 
  separate(col=Date, into=c('Year', 'Month', "Day"), sep='-')
```

## Exercise

### Exercise 1:

```{r}
avocado |>
  semi_join(y = avocado_major_regions, by = "region") |> 
  filter(type == "organic", Year == 2017) |> 
  group_by(region) |> 
  summarise(sum_small_total_volume = sum(small))
```

### Answer:

The West Region sold the most organic, small Hass avocados in 2017

### Exercise 2:

```{r}
avocado |> 
  select(Month, `Total Volume`) |> 
  group_by(Month) |> 
  summarise(`Total Per Month` = sum(`Total Volume`)) |> 
  slice_max(`Total Per Month`)

```

### Answer:

February is the month with the highest volume of avocado sales.

### Exercise 3:

```{r}
##Filtering Dataset To Just Metro Areas
Metro_Avocado_Only <- avocado |> 
  anti_join(avocado_major_regions, by = "region") |> 
  anti_join(avocado_cali_regions, by = "region") |> 
  anti_join(avocado_states, by = "region") |> 
  filter(region != "TotalUS")

##Calculations
Metro_Top5 <- Metro_Avocado_Only |> 
  group_by(region) |> 
  summarize("Sum Total Volume" = sum(`Total Volume`)) |> 
  arrange(desc(`Sum Total Volume`)) |> 
  slice_head(n = 5)

#Plotting
Metro_Avocado_Only |> 
  semi_join(Metro_Top5, by = "region") |> 
  ggplot(mapping = aes(x = `Total Volume`, y = region))+
  geom_boxplot()+
  labs(x = "Total Volume Of Avocado Sales", y = "Top Five Metro Areas")
  
```

### Answer:

Phoenix/Tucson, Houston, Denver, Dallas/FtWorth, and Baltimore sold the most total avocados.

### Reshaping

#### Creating Reshaping Data

```{r}
#| message: false
#| warning: false
organic_vs_conventional_avocado <- avocado |>
  semi_join(avocado_cali_regions, by = "region") |> 
  group_by(region, type) |> 
  summarise(avg_avocado_price = mean(AveragePrice)) |> 
  pivot_wider(names_from = "type", values_from = "avg_avocado_price") |> 
  mutate(`Difference In Avg Price For Conventional and Organic` = organic - conventional)

ggplot(organic_vs_conventional_avocado, aes(x = region,
    y = `Difference In Avg Price For Conventional and Organic`))+
geom_point()

```

### Answer:

San Francisco has the highest average price difference between conventional and organic Avocados! This is shown by the two graphs above, where the top plots the mean avocado price for both conventional and organic, while the bottom plot simply plots the difference between the two.

```{r}
proportion_avocado_data <- avocado |>
  semi_join(avocado_cali_regions, by = "region") |> 
  pivot_longer("small":"extralarge",
               names_to = "Avocado Size",
               values_to = "Number Of Avocados") |> 
  mutate(Proportion = `Number Of Avocados` / mean(`Total Volume`))

proportion_avocado_data |> 
  ggplot(mapping = aes(x = region, y = Proportion, fill = `Avocado Size`))+
  geom_bar(position = position_fill(reverse = TRUE), stat = "identity") +
  labs(x = "Regions of CA", y = "Proportion of Mean Avocados Sold") + 
  ##Function was shown to me on discord lab chat and found in stack overflow
  scale_x_discrete(guide = guide_axis(n.dodge=2))+
  facet_wrap(~type)
  

```
