---
title: "Andrew Martinez Stat 331 Challenge 3"
format:
  html:
    code-fold: true
  
editor: visual
---

## Challenge 3 Hip-Hop Lyrics

### Declaring Libraries

```{r}
#| message = FALSE
library(tidyverse)
```

### Loading In Data

```{r}
#| message = FALSE
library(here)
hiphop = read.csv(here::here("supporting_artifacts", "Lab & Challenge 3", 
                             "hiphop.csv"))
```

### Part A

```{r}
gender_hiphop <- hiphop |> 
  group_by(sex) |> 
  distinct(subj, .keep_all = TRUE) |> 
  summarize(across(intl:unclassifiable, mean)) |> 
  summarize(across(intl:unclassifiable, diff))


gender_hiphop
```

### Conclusion:

The largest difference in preference between Females and Males is Rock. The average for Males is 3.06, compared to an average of 1.9 for Females.

### Part B

### Ethnic

```{r}
ethnic_hiphop <- hiphop |> 
  mutate(ethnic_categorical = ifelse(ethnic == "white", 
                         "white", 
                         "non-white")) |> 
  group_by(ethnic_categorical) |> 
  distinct(subj, .keep_all = TRUE) |>
  summarize(across(intl:unclassifiable, mean)) |> 
  summarize(across(intl:unclassifiable, diff))
  
ethnic_hiphop
```

### Conclusion:

When comparing White to Non-White:

Intl: Significantly higher for Non-White

Rock: Significantly higher for White

Alternative: Significantly higher for White

HipHop: Significnatly higher for Non-White

### Study Design Critique

-   Participants were students at a university: Not inclusive of students outside of university, especially since students who attend university display different characteristics and backgrounds to young adolescents who do not attend university.

-   Participants were students at a university in Minnesota: Students were only selected in Minnesota, this poses another sampling issue. The average student in Minnesota is likely different than the average student in the USA, so this poses a sampling problem that would skew the results of this data!
