---
title: "Lab1"
author: "Andrew Martinez"
format:
  html:
    fontcolor: 'red'
    font-family: Georgia
    code-fold: True
editor: visual
---

Changes: Changed all of the font to Georgia in HTML, also changed the font color to red.

## Summarizing The Cars Data Set

This data set contains information about Cars. The data was collected in 1920s.It has 50 rows and 2 variables.

```{r}
summary(cars)
```

## Creating & Labeling The Pressure Data Set

This chunk of R code displays a plot of the Pressure data set! This includes a scatter plot of Temperature, measured in Celsius, on the X axis and Pressure on the Y Axis.

```{r}
#| label: fig-pressure
#| fig-cap-location: top
#| fig-cap: "Scatter Plot of Pressure & Temperature"
#| fig-align: center

pressure_plot <- plot(pressure, xlab = "Temperature (C)", ylab = "Pressure (mm)")

```

## Creating & Labeling Scatter Plots For The Cars Data Set

Similarly to the prior R code chunk, this chunk of code will display scatter plots. However, the data set utilized is Cars, which analyzes the relationship between Speed in MPH, and Stopping Distance in feet.

1)  Add Color to the Plot

2)  Have a title for the scatter plot.

```{r}
#| label: fig-cars
#| layout-ncol: 2
dist <- cars$dist
hist(dist, xlab = "Stopping Distance (Feet)", ylab = "Frequency", main = "Frequency of Stopping Distances In Feet", col = "blue")
plot(cars, xlab = "Speed (MPH)", ylab = "Stopping Distance (Feet)")
```
